### 2020-12-14 README.Rmd
tidy_dist_mat and calculation of new observation's depth / psuedo-densities relative to another set of observations (part 3): check passing

    c. Finally, we've also leveraged ideas from [R-devel: on avoiding problems with `:::`](https://stat.ethz.ch/pipermail/r-devel/2013-August/067210.html) in `R/aaa.R` to overcome messages from CRAN relative to this hack (using `:::`). For some reason - when documenting for `pkgdown` website, we need to do `library(ggtern); EpiCompare:::update_approved_layers()`
3. `geom_prediction_band` required not just `compute_group` but `compute_layer` - there is very little documentation on how to approach this correctly. Basically - there are problems when the `compute_group` wants to make multiple `pieces`/`groups` - and it is similar to the problem that if you do something like `aes(color = var1, group = var2)` you may actually want to do `aes(color = var1, group = paste(var1, var2))`, if there are the same `var2` values across different `var1` values but they don't mean they should be grouped together.
4. Now that `R` have come out with version >= 4.0.0, we now need to call `.S3method("method", "class")` to define the connection for `S3` methods (e.g. `method.class` function), which we have for the `contained` function. 
5. **Does 2 wrongs make a right?** As of 9/23 `ggtern` had an [issue](https://bitbucket.org/nicholasehamilton/ggtern/issues/13/ggtern-breaks-ggplots-plot) that it messed with `ggplot2`'s legends when loaded (it over-wrote the `print.ggplot` and other functions). To "correct" this, we've over-wrote `ggtern`'s `print.ggplot` to correct this problem when not producing ternary plots (code in `aaa.R`). 
6. Useful Rstudio shortcuts for `Roxygen2`: (a) create `Roxygen2` comments template with `option` + `command` + `shift` + `R` (b) In `Roxygen2` comments do `control` + `shift` + `/` to format relative to 80 char limit.
7.[stack overflow](https://stackoverflow.com/questions/11285496/r-cmd-check-warning-functions-methods-with-usage-in-documentation-object-bu) post on how to pass `check` for `rownames<-.tidy_dist_mat`.

>>>>

    c. Finally, we've also leveraged ideas from [R-devel: on avoiding problems with `:::`](https://stat.ethz.ch/pipermail/r-devel/2013-August/067210.html) in `R/aaa.R` to overcome messages from CRAN relative to this hack (using `:::`). For some reason - when documenting for `pkgdown` website, we need to do `library(ggtern); EpiCompare:::update_approved_layers()`
3. `geom_prediction_band` required not just `compute_group` but `compute_layer` - there is very little documentation on how to approach this correctly. Basically - there are problems when the `compute_group` wants to make multiple `pieces`/`groups` - and it is similar to the problem that if you do something like `aes(color = var1, group = var2)` you may actually want to do `aes(color = var1, group = paste(var1, var2))`, if there are the same `var2` values across different `var1` values but they don't mean they should be grouped together.
4. Now that `R` have come out with version >= 4.0.0, we now need to call `.S3method("method", "class")` to define the connection for `S3` methods (e.g. `method.class` function), which we have for the `contained` function. 
5. **Does 2 wrongs make a right?** As of 9/23 `ggtern` had an [issue](https://bitbucket.org/nicholasehamilton/ggtern/issues/13/ggtern-breaks-ggplots-plot) that it messed with `ggplot2`'s legends when loaded (it over-wrote the `print.ggplot` and other functions). To "correct" this, we've over-wrote `ggtern`'s `print.ggplot` to correct this problem when not producing ternary plots (code in `aaa.R`). 
6. Useful Rstudio shortcuts for `Roxygen2`: (a) create `Roxygen2` comments template with `option` + `command` + `shift` + `R` (b) In `Roxygen2` comments do `control` + `shift` + `/` to format relative to 80 char limit.
7. [stack overflow](https://stackoverflow.com/questions/11285496/r-cmd-check-warning-functions-methods-with-usage-in-documentation-object-bu) post on how to pass `check` for `rownames<-.tidy_dist_mat`.
